---
output: rmarkdown::github_document
---

`bloomsky` : Tools to Work with 'BloomSky' Weather Station Data

The 'BloomSky' weather station has a cloud service <https://www.bloomsky.com/> that centralizes data
collection and provides a user interface for interactive data viewing as well as an 'API'. Tools are 
provided to work with the underlying weather data feeds from the site.

The following functions are implemented:

- `bsky_public_station_data`:	Retrieve current reading from a single BloomSky station
- `bsky_get_reading`:	Retrieve last, current station reading

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/bloomsky")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(bloomsky)
library(tidyverse)

# current verison
packageVersion("bloomsky")

wx_dat <- bsky_public_station_data("gqBxp6apnJSnmpym")

glimpse(wx_dat)
```

```{r eval=FALSE}
bsky_get_reading()
```

```{r eval=TRUE, echo=FALSE}
bsky_get_reading() %>% 
  select(-fulladdress, -streetname, -deviceid)
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(bloomsky)
library(testthat)

date()

test_dir("tests/")
```

